\huge A Usability Evaluation of Tor Launcher

### 2016-10-21 pets2017-paper/pets2017-paper.tex
minor wording tweaks

\section{Background}
\label{sec:background}
This section talks about network components involved in connecting to Tor, network conditions that require these network components, and examples of what users must currently do to connect to Tor.

@@

For our experiments, we use instrumented versions of Tor Browser~5.0.3, 
the most recent stable release at the time~\cite{torbrowser-503}.
Though there were new releases during the experiments,
we used the same version across all participants to not introduce
confounding factors.

>>>>

\section{Background}
\label{sec:background}
This section discusses network components involved in connecting to Tor, network conditions that require these network components, and the set of valid ways to connect to Tor.

@@

For our experiments, we use versions of Tor Browser~5.0.3, 
the most recent stable release at the time~\cite{torbrowser-503}.
Though there were new releases during the experiments,
we used the same version across all participants to not introduce
confounding factors.
